### 2016-09-28 R/ITHIM.Rmd
Worked on state-wise figures

@@

```{r NHTS, eval = TRUE, echo = FALSE}
DAYV2PUB <- read.csv(file = "~/GHI/data/NHTS/Ascii/DAYV2PUB.CSV", na.strings = c("-9","-8", "-7", "-1"))
names(DAYV2PUB) <- c("HOUSEID","PERSONID","FRSTHM","OUTOFTWN","ONTD_P1","ONTD_P2","ONTD_P3","ONTD_P4","ONTD_P5","ONTD_P6","ONTD_P7","ONTD_P8","ONTD_P9","ONTD_P10","ONTD_P11","ONTD_P12","ONTD_P13","ONTD_P14","ONTD_P15","TDCASEID","HH_HISP","HH_RACE","DRIVER","R_SEX","WORKER","DRVRCNT","HHFAMINC","HHSIZE","HHVEHCNT","NUMADLT","FLAG100","LIF_CYC","TRIPPURP","AWAYHOME","CDIVMSAR","CENSUS_D","CENSUS_R","DROP_PRK","DRVR_FLG","EDUC","ENDTIME","HH_ONTD","HHMEMDRV","HHRESP","HHSTATE","HHSTFIPS","INTSTATE","MSACAT","MSASIZE","NONHHCNT","NUMONTRP","PAYTOLL","PRMACT","PROXY","PSGR_FLG","R_AGE","RAIL","STRTTIME","TRACC1","TRACC2","TRACC3","TRACC4","TRACC5","TRACCTM","TRAVDAY","TREGR1","TREGR2","TREGR3","TREGR4","TREGR5","TREGRTM","TRPACCMP","TRPHHACC","TRPHHVEH","TRPTRANS","TRVL_MIN","TRVLCMIN","TRWAITTM","URBAN","URBANSIZE","URBRUR","USEINTST","USEPUBTR","VEHID","WHODROVE","WHYFROM","WHYTO","WHYTRP1S","WRKCOUNT","DWELTIME","WHYTRP90","TDTRPNUM","TDWKND","TDAYDATE","TRPMILES","WTTRDFIN","VMT_MILE","PUBTRANS","HOMEOWN","HOMETYPE","HBHUR","HTRESDN","HTHTNRNT","HTPPOPDN","HTEEMPDN","HBRESDN","HBHTNRNT","HBPPOPDN","GASPRICE","VEHTYPE","HH_CBSA","HHC_MSA")

NHTS.trips <- with(DAYV2PUB,{
    data.frame(HOUSEID = HOUSEID,
                   PERSONID = PERSONID,
                   TDCASEID = TDCASEID,
                   AT = ifelse(TRPTRANS == "22", "cycle",
                        ifelse(TRPTRANS == "23", "walk",
                        ifelse(!is.na(TRPTRANS), "other", NA))),
                   TRVL_MIN = as.numeric(TRVL_MIN),
                   TRVLCMIN = ifelse(as.numeric(TRVLCMIN) != 0, as.numeric(TRVLCMIN), NA),
                   URBRUR  = as.factor(URBRUR),
                   #HHSTATE = as.factor(HHSTATE),
                   MSACAT = as.factor(MSACAT),
                   MSA = ifelse(MSASIZE %in% 1:5, TRUE, FALSE),
                   TRPTRANS = as.factor(TRPTRANS),
                   TRPMILES = as.numeric(TRPMILES)
)})

@@

#### Investigate Trip Data

```{r summary, fig.width = 20, fig.height = 10, eval = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
walkHours <- with(subset(NHTS.trips, {
    AT == "walk" & TRPMILES < 10 & TRPMILES/TRVL_MIN*60 < 8 & TRVL_MIN > 5 #& TRPMILES/TRVL_MIN*60 > 0.5
}), TRVL_MIN/60)

@@

How do we merge?  Are there people who were surveyed who had zero
travel time?  Couldnt have been very many.  But I think there are
people in the PERSON table that were not interviewed.

```{r subset, eval = TRUE, fig.width = 10, echo = FALSE}
NHTS.person <- subset( NHTS.person, MSA == TRUE & HHSTATE %in% c("CA","TX","NY","FL","VA","NC","AZ"))
NHTS <- merge(NHTS.person, NHTS.trips, by = c("HOUSEID","PERSONID"))
```

@@

@@

```{r ITHIMObjs, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = FALSE, warning = FALSE}
upper <- 100
length <- 10

## D1 <- subset(D, Region %in% c("HHS01","HHS02","HHS09","HHS10","National") & ageClass != "1" )
## D2 <- subset(D, !(Region %in% c("HHS01","HHS02","HHS09","HHS10")) & ageClass != "1" )

p <- ggplot(D, aes(x = ageClass, y = time, fill = Sex)) + geom_bar(stat= "identity", position = "dodge") 
p + theme_bw() + scale_x_discrete(name="Age Class", breaks = c(2,4,6,8)) + scale_y_continuous(name="Travel Time per Week (minutes)") + facet_grid( mode ~ State, scales = "free_y")

## p2 <- ggplot(D2, aes(x = ageClass, y = time, fill = Sex)) + geom_bar(stat= "identity", position = "dodge") 
## p2 + theme_bw() + scale_x_discrete(name="Age Class", breaks = c(2,4,6,8)) + scale_y_continuous(name="Travel Time per Week (minutes)") + facet_grid( mode ~ Region, scales = "free_y")

```{r California, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}
ITHIM.CA <- ITHIMList[["CA"]]
ITHIM.CA <- updateITHIM(ITHIM.CA, parName = "muNonTravel", 10)
ITHIM.national <- updateITHIM(ITHIM.national, parName = "muNonTravel", 10)
foo <- compareModels(ITHIM.national,ITHIM.CA)
foobar <- data.frame(cbind(melt(foo$daly.delta),paste0("ageClass",1:8)))
names(foobar) <- c("delta.DALY","Sex","Disease","ageClass")
p <- ggplot( foobar, aes(ageClass,-delta.DALY/1e3, fill = Sex) )
p + geom_bar(stat="identity", position = "dodge") + scale_x_discrete(name="Age Class", breaks = c(2,4,6,8)) + scale_y_continuous(name="DALYs Averted Nationwide (Thousands)") + facet_grid( . ~ Disease) + theme_bw() 
```

@@

```{r instantiate, eval = TRUE, echo = FALSE}
ITHIM.baseline <- createITHIM(vision = "baseline", region = "SFBayArea")
ITHIM.scenario <- createITHIM(vision = "scenario", region = "SFBayArea")
```

@@

```{r RRs, eval = TRUE, echo = FALSE}
comparativeRisk <- compareModels(ITHIM.baseline,ITHIM.scenario)
```

### Deaths
```{r show, echo = FALSE, eval = TRUE, echo = FALSE}
matrix(unlist(lapply(comparativeRisk$dproj.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```
### DALY
```{r show2, echo = FALSE, eval = TRUE, echo = FALSE}
matrix(unlist(lapply(comparativeRisk$daly.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```
### YLD
```{r show3, echo = FALSE, eval = TRUE, echo = FALSE}
matrix(unlist(lapply(comparativeRisk$yld.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```
### YLL
```{r show4, echo = FALSE, eval = TRUE, echo = FALSE}
matrix(unlist(lapply(comparativeRisk$yll.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```

@@

```{r instantiate2, eval = TRUE, echo = FALSE}
ITHIM.baseline <- createITHIM(vision = "baseline", region = "national")
ITHIM.scenario <- createITHIM(vision = "scenario", region = "national")
```

```{r RRs2, eval = TRUE, echo = FALSE}
comparativeRisk <- compareModels(ITHIM.baseline,ITHIM.scenario)
```

### Deaths
```{r show222, echo = FALSE, eval = TRUE}
matrix(unlist(lapply(comparativeRisk$dproj.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```
### DALY
```{r show22, echo = FALSE, eval = TRUE}
matrix(unlist(lapply(comparativeRisk$daly.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```
### YLD
```{r show23, echo = FALSE, eval = TRUE}
matrix(unlist(lapply(comparativeRisk$yld.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```
#### YLL
```{r show24, echo = FALSE, eval = TRUE}
matrix(unlist(lapply(comparativeRisk$yll.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```

@@

```{r example, eval = TRUE, echo = FALSE}
example("ITHIM-package")
```

@@

```{r vision, eval = TRUE, echo = FALSE}
ITHIM.vision <- updateITHIM(ITHIM.scenario, "muwt", 2*ITHIM.scenario$parameters$muwt) # Double the mean walking time
comparativeRisk <- compareModels(ITHIM.baseline,ITHIM.vision)
```
#### YLL
```{r show233, echo = FALSE, eval = TRUE}
matrix(unlist(lapply(comparativeRisk$yll.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```

@@

```{r params, eval = TRUE, echo = FALSE}
names(ITHIM.baseline$parameters)
ITHIM.baseline$parameters$NonTravelMETs
ITHIM.baseline$parameters$Rwt
```

@@

NHTS %>% group_by(HOUSEID, PERSONID) %>% dplyr::summarise( n = n()) # 260,576 people in merged data

#NHTS <- subset(NHTS, !is.na(AGE) & !is.na(SEX))

ggplot(NHTS, aes(x = TRVL_MIN, ..density.., colour = AGE)) + geom_freqpoly(binwidth = 15) + facet_grid( SEX ~ AT) + labs(x = "Foo", colour = "Age") + coord_cartesian(xlim = c(0, 75))

NHTS %>% group_by(SEX, AGE) %>% dplyr::summarize(count = countPeople(data.frame(HOUSEID = HOUSEID, PERSONID = PERSONID)))
```

>>>>

```{r compute, echo = FALSE, eval = TRUE}
compute <- FALSE
```

@@

```{r NHTS, eval = compute, echo = FALSE}
DAYV2PUB <- read.csv(file = "~/GHI/data/NHTS/Ascii/DAYV2PUB.CSV", na.strings = c("-9","-8", "-7", "-1"))
names(DAYV2PUB) <- c("HOUSEID","PERSONID","FRSTHM","OUTOFTWN","ONTD_P1","ONTD_P2","ONTD_P3","ONTD_P4","ONTD_P5","ONTD_P6","ONTD_P7","ONTD_P8","ONTD_P9","ONTD_P10","ONTD_P11","ONTD_P12","ONTD_P13","ONTD_P14","ONTD_P15","TDCASEID","HH_HISP","HH_RACE","DRIVER","R_SEX","WORKER","DRVRCNT","HHFAMINC","HHSIZE","HHVEHCNT","NUMADLT","FLAG100","LIF_CYC","TRIPPURP","AWAYHOME","CDIVMSAR","CENSUS_D","CENSUS_R","DROP_PRK","DRVR_FLG","EDUC","ENDTIME","HH_ONTD","HHMEMDRV","HHRESP","HHSTATE","HHSTFIPS","INTSTATE","MSACAT","MSASIZE","NONHHCNT","NUMONTRP","PAYTOLL","PRMACT","PROXY","PSGR_FLG","R_AGE","RAIL","STRTTIME","TRACC1","TRACC2","TRACC3","TRACC4","TRACC5","TRACCTM","TRAVDAY","TREGR1","TREGR2","TREGR3","TREGR4","TREGR5","TREGRTM","TRPACCMP","TRPHHACC","TRPHHVEH","TRPTRANS","TRVL_MIN","TRVLCMIN","TRWAITTM","URBAN","URBANSIZE","URBRUR","USEINTST","USEPUBTR","VEHID","WHODROVE","WHYFROM","WHYTO","WHYTRP1S","WRKCOUNT","DWELTIME","WHYTRP90","TDTRPNUM","TDWKND","TDAYDATE","TRPMILES","WTTRDFIN","VMT_MILE","PUBTRANS","HOMEOWN","HOMETYPE","HBHUR","HTRESDN","HTHTNRNT","HTPPOPDN","HTEEMPDN","HBRESDN","HBHTNRNT","HBPPOPDN","GASPRICE","VEHTYPE","HH_CBSA","HHC_MSA")

NHTS.trips <- with(DAYV2PUB,{
    data.frame(HOUSEID = HOUSEID,
                   PERSONID = PERSONID,
                   TDCASEID = TDCASEID,
                   AT = ifelse(TRPTRANS == "22", "cycle",
                        ifelse(TRPTRANS == "23", "walk",
                        ifelse(!is.na(TRPTRANS), "other", NA))),
                   TRVL_MIN = as.numeric(TRVL_MIN),
                   TRVLCMIN = ifelse(as.numeric(TRVLCMIN) != 0, as.numeric(TRVLCMIN), NA),
                   URBRUR  = as.factor(URBRUR),
                   MSACAT = as.factor(MSACAT),
                   MSA = ifelse(MSASIZE %in% 1:5, TRUE, FALSE),
                   TRPTRANS = as.factor(TRPTRANS),
                   TRPMILES = as.numeric(TRPMILES)
)})

@@

```{r summary, fig.width = 20, fig.height = 10, eval = compute, echo = FALSE, message = FALSE, warning = FALSE}
walkHours <- with(subset(NHTS.trips, {
    AT == "walk" & TRPMILES < 10 & TRPMILES/TRVL_MIN*60 < 8 & TRVL_MIN > 5 #& TRPMILES/TRVL_MIN*60 > 0.5
}), TRVL_MIN/60)

@@

The PERSON table contains the family members of the person surveyed,
right?  We want only the peole who were surveyed for their travel
times.  So, we can\'t use everyone in the PERSON table.  If someone
had zero trip time they would not exist in the TRIP table.  So, if we
use just the TRIP table we miss people with zero trip time. So how do
we merge?  We use an inner join and assume that their is a negligible
number of people with zero trip time.  Not very many people never stay
in the house all day.  Please correct me if I am mistaken abiout the
nature of the PERSON or TRIP tables.

```{r subset, eval = compute, fig.width = 10, echo = FALSE}
NHTS.person <- subset( NHTS.person, MSA == TRUE & HHSTATE %in% c("CA","TX","NY","FL","VA","NC","AZ"))
NHTS <- merge(NHTS.person, NHTS.trips, by = c("HOUSEID","PERSONID"))
saveRDS(NHTS, file = "./data/NHTS.rds")
```

```{r loadNHTS, eval = !compute}
NHTS <- readRDS(file = "./data/NHTS.rds")
```

@@

```{r ITHIMObjs, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = TRUE, warning = FALSE}
upper <- 25; wd <- 1; length <- upper/wd + 1;

p <- ggplot(subset(D,ageClass != 1), aes(x = ageClass, y = time, fill = Sex)) + geom_bar(stat= "identity", position = "dodge") 
p + theme_bw() + scale_x_discrete(name="", labels = c("5-14","15-29","30-44","45-59","60-69","70-79","80+")) + scale_y_continuous(name="Travel Time per Week (minutes)") + facet_grid( mode ~ State, scales = "free_y") + theme(axis.text.x  = element_text(angle = 90, vjust = 0.5, size = 5))

```{r California, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}

ITHIM.national <- updateITHIM(ITHIM.national, parName = "muNonTravel", 10)

ITHIM.CA <- ITHIMList[["CA"]]
ITHIM.CA <- updateITHIM(ITHIM.CA, parName = "muNonTravel", 10)
foo1 <- compareModels(ITHIM.national,ITHIM.CA)
foobar1 <- data.frame(cbind(melt(foo1$daly.delta),paste0("ageClass",1:8)),State = "CA")

ITHIM.NY <- ITHIMList[["NY"]]
ITHIM.NY <- updateITHIM(ITHIM.NY, parName = "muNonTravel", 10)
foo2 <- compareModels(ITHIM.national,ITHIM.NY)
foobar2 <- data.frame(cbind(melt(foo2$daly.delta),paste0("ageClass",1:8)),State = "NY")

foobar <- rbind(foobar1,foobar2)
names(foobar) <- c("delta.DALY","Sex","Disease","ageClass","State")

foobar <- within(foobar, {
  Disease[Disease == "BreastCancer"] <- "Breast"
  Disease[Disease == "ColonCancer"] <- "Colon"
  Disease <- factor(Disease, levels = c("Breast", "Colon", "Dementia", "Depression", "Diabetes"))
})

p <- ggplot( subset(foobar,ageClass != "ageClass1"), aes(ageClass,-delta.DALY/1e3, fill = Sex) )
p + geom_bar(stat="identity", position = "dodge") + scale_x_discrete(name="", labels = c("5-14","15-29","30-44","45-59","60-69","70-79","80+")) + scale_y_continuous(name="DALYs Averted Nationwide (Thousands)") + facet_grid( State ~ Disease) + theme_bw() + theme(axis.text.x  = element_text(angle=90, vjust=0.5, size=8))
```

```{r counts, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}
D <- melt(counts)
names(D) <- c("count","AgeClass","Sex", "State")
D <- within(D,{
  State <- factor(State, levels = c("NC","TX","VA","FL","AZ","NY","CA","Natl."))
  Sex <- factor(Sex, levels = c("F","M"))
})
p <- ggplot(subset(D,AgeClass != "00-04"), aes(AgeClass, count/1e3, fill = Sex))
p + geom_bar(stat="identity", position = "dodge") + scale_x_discrete(name="", labels = c("5-14","15-29","30-44","45-59","60-69","70-79","80+")) + scale_y_continuous(name="Individuals Sampled (Thousands)") + facet_grid( . ~ State) + theme_bw() + theme(axis.text.x  = element_text(angle=90, vjust=0.5, size=6))
```

@@

@@

```{r instantiate, eval = FALSE, echo = FALSE}
ITHIM.baseline <- createITHIM(vision = "baseline", region = "SFBayArea")
ITHIM.scenario <- createITHIM(vision = "scenario", region = "SFBayArea")
```

@@

```{r RRs, eval = FALSE, echo = FALSE}
comparativeRisk <- compareModels(ITHIM.baseline,ITHIM.scenario)
```

### Deaths
```{r show, echo = FALSE, eval = FALSE, echo = FALSE}
matrix(unlist(lapply(comparativeRisk$dproj.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```
### DALY
```{r show2, echo = FALSE, eval = FALSE, echo = FALSE}
matrix(unlist(lapply(comparativeRisk$daly.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```
### YLD
```{r show3, echo = FALSE, eval = FALSE, echo = FALSE}
matrix(unlist(lapply(comparativeRisk$yld.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```
### YLL
```{r show4, echo = FALSE, eval = FALSE, echo = FALSE}
matrix(unlist(lapply(comparativeRisk$yll.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```

@@

```{r instantiate2, eval = FALSE, echo = FALSE}
ITHIM.baseline <- createITHIM(vision = "baseline", region = "national")
ITHIM.scenario <- createITHIM(vision = "scenario", region = "national")
```

```{r RRs2, eval = FALSE, echo = FALSE}
comparativeRisk <- compareModels(ITHIM.baseline,ITHIM.scenario)
```

### Deaths
```{r show222, echo = FALSE, eval = FALSE}
matrix(unlist(lapply(comparativeRisk$dproj.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```
### DALY
```{r show22, echo = FALSE, eval = FALSE}
matrix(unlist(lapply(comparativeRisk$daly.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```
### YLD
```{r show23, echo = FALSE, eval = FALSE}
matrix(unlist(lapply(comparativeRisk$yld.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```
#### YLL
```{r show24, echo = FALSE, eval = FALSE}
matrix(unlist(lapply(comparativeRisk$yll.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```

@@

```{r example, eval = FALSE, echo = FALSE}
example("ITHIM-package")
```

@@

```{r vision, eval = FALSE, echo = FALSE}
ITHIM.vision <- updateITHIM(ITHIM.scenario, "muwt", 2*ITHIM.scenario$parameters$muwt) # Double the mean walking time
comparativeRisk <- compareModels(ITHIM.baseline,ITHIM.vision)
```
#### YLL
```{r show233, echo = FALSE, eval = FALSE}
matrix(unlist(lapply(comparativeRisk$yll.delta,function(x) lapply(x, function(x) sum(x[-(1:2)]) ))),nrow=5,ncol=2,byrow=TRUE,dimnames=list(names(comparativeRisk$dproj.delta),c("M","F")))
```

@@

```{r params, eval = FALSE, echo = FALSE}
names(ITHIM.baseline$parameters)
ITHIM.baseline$parameters$NonTravelMETs
ITHIM.baseline$parameters$Rwt
```

@@

NHTS %>% group_by(HOUSEID, PERSONID) %>% dplyr::summarise( n = n()) # 260,576 people in merged data
ggplot(NHTS, aes(x = TRVL_MIN, ..density.., colour = AGE)) + geom_freqpoly(binwidth = 15) + facet_grid( SEX ~ AT) + labs(x = "Foo", colour = "Age") + coord_cartesian(xlim = c(0, 75))
NHTS %>% group_by(SEX, AGE) %>% dplyr::summarize(count = countPeople(data.frame(HOUSEID = HOUSEID, PERSONID = PERSONID)))
```
